---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# winaRaque

<!-- badges: start -->
[![R-CMD-check](https://github.com/Alexis-vs/winaRaque/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/Alexis-vs/winaRaque/actions/workflows/R-CMD-check.yaml)
[![Scrape NBA matchs](https://github.com/Alexis-vs/winaRaque/actions/workflows/nba_matchs_scrap.yml/badge.svg)](https://github.com/Alexis-vs/winaRaque/actions/workflows/nba_matchs_scrap.yml)
<!-- badges: end -->

The goal of winaRaque is to explore sport data and make analysis with sport betting odds. The first analyzes will be done through the NBA.

## Installation

You can install the development version of winaRaque from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Alexis-vs/winaRaque")
```

## Example

You can get NBA results with 1/2 odds for a day.

```{r example}
library(winaRaque)

get_nba_scores("2023-03-23", pivot_results = TRUE)
```


## Small data visualization

```{r}
# the workflow has been taking the odds since 2023-03-20
seq_date <- seq.Date(from = as.Date("2023-03-19"),
                     to = as.Date("2023-04-05"),
                     by = "day")
list_results <- lapply(seq_date, get_nba_scores, pivot_results = TRUE)
results <- do.call("rbind", list_results)
```

```{r, message=FALSE, warning=FALSE}
library(ggplot2)
library(dplyr)

results %>%
  ggplot(aes(x = Name, y = Odd, color = WINLOSE)) +
  geom_boxplot() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5)) +
  ggtitle("Odds distribution according to result", subtitle = "by teams")
```


## Data collect

A workflow run everyday to get all NBA odds for the night (currently stopped because no NBA matchs). The results are in `inst/extdata`.  
An other workflow run every morning to collect odds for shiny app.

## Shiny

Shiny app to explore 'surbet' variations during games of 1/2 sports (tennis, basketball, baseball). Run the Shiny app with `app.R`.
