---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# winaRaque

<!-- badges: start -->
[![R-CMD-check](https://github.com/Alexis-vs/winaRaque/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/Alexis-vs/winaRaque/actions/workflows/R-CMD-check.yaml)
[![Scrape NBA matchs](https://github.com/Alexis-vs/winaRaque/actions/workflows/nba_matchs_scrap.yml/badge.svg)](https://github.com/Alexis-vs/winaRaque/actions/workflows/nba_matchs_scrap.yml)
<!-- badges: end -->

The goal of winaRaque is to explore sport data and make analysis with sport betting odds. The first analyzes will be done through the NBA.

## Installation

You can install the development version of winaRaque from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Alexis-vs/winaRaque")
```

## Example

You can get NBA results for a day.

```{r example}
library(winaRaque)

get_nba_scores("2023-01-21")
```


## Data collect

A workflow run everyday to get all NBA odds for the night. The results are in `inst/extdata`.
